Towards user-friendliness in proof assistants: automated strategies \textbf{via} algebraic effects and handlers

### 2020-09-18 paper/main.tex
related work

\title[Towards user-friendliness in theorem provers]{Towards user-friendliness
  in proof assistants: automated strategies \textbf{via} algebraic effects and handlers}

@@

While it is hard to say whether we have achieve our goals before user
evaluations, Witch steps towards a future where proof assistants are
friendlier towards users, particularly newcomers. The present work is in its
infancy, and there are many issues concerning Witch's ability to guide newcomers
towards correct-by-construction software, which constitutes the main improvement
we intend for Witch. We hypothesise about the possibility of using proof
reconstruction, therefore relocating Witch to an assistant that lives solely
within the interactive mode -- as opposed to a framework for proof
automation in user code.

>>>>

\title[Towards user-friendliness in proof assistants]{Towards user-friendliness
  in proof assistants: automated strategies \textbf{via} algebraic effects and handlers}

@@

\subsection{Comparison with Similar Approaches}

\paragraph{Andromeda proof assistant} As mentioned, this project was inspired by the
Andromeda proof assistant. It follows the LCF tradition of theorem provers,
where there exist two distinct languages. One habits a safe nucleus that
verifies hypotheses, on the other hand, the second hand comprises a polymorphic
$\lambda$ calculus where users implement their theories and relay the
verification to the nucleus.

\paragraph{Meta-F*} F* is a dependently typed language with (monadic) effects and liquid
types. For tactics, F* uses a library called Meta-F*, where tactics are
considered an effect that uses meta-programming provided by the typechecker to
manipulate proof objects. Agda's Witch implementation is heavily inspired by Meta-F*.

\paragraph{Mtac and Cybele} The idea of proof strategies happening within an
effectful structure was first introduced in Cybele and later extended into Mtac.
Mtac extends Coq's powerful main language, providing the user with a
dependently-typed tactic language.

\subsection{Improving Witch Further}
While it is hard to say whether we have achieve our goals before user
evaluations, Witch steps towards a future where proof assistants are
friendlier towards users, particularly newcomers. The present work is in its
infancy, and there are many issues concerning Witch's ability to guide newcomers
towards correct-by-construction software, which constitutes the main improvement
we intend for Witch. We hypothesise about the possibility of using proof
reconstruction, therefore relocating Witch to an assistant that lives solely
within the interactive mode -- as opposed to a framework for proof
automation in user code.
